Mathematical Approaches for Simulating Epidemic Progression: Addressing Limitations of the Linear Chain Trick in ODE Models

### 2024-03-29 thesis/draft.tex
temp storage
modify makefile for newplot depend on tempfunc
I think I broke Makefile...

@@

@@

@@

\subsection{Adaptability of the GCT Model to Data Input and Structural Changes in Fitting}
Proceeding to a more challenging test, we utilized a different model type for data generation and model fitting. As demonstrated in Figure x.x, the data generated by the LCT model with 2 substages were fitted using the GCT model with 12 substages. Despite the significant difference in model structure, the fitting results were reasonably favorable, with an MSE of 2.4. Altering the fitting model from a GCT with 2 substages to a GCT with 6 substages had negligible impact on the fitting outcomes (Figure x.x). Similarly, changing the input data from an LCT with 2 substages to an LCT with 7 substages resulted in slightly improved fitting, though the difference was not substantial (Figure x.x). These findings suggest that regardless of changes to the fitting model structure or the data used, the GCT model is capable of adapting to these variations, providing satisfactory fitting results.

\subsection{Parameter Estimation}
In this section, we discuss the parameter estimation results obtained through model fitting. The incidence data were generated using the GCT model with 6 substages, setting the $D$ to 10 and $\kappa$ to $\frac{2}{9}$. The model was fitted using the GCT framework with 2 to 10 substages. As depicted in Figure x.x, the precise values for each parameter are marked by a red line, with post-fitting parameter values displayed alongside their 95\% confidence intervals. It can be observed that the parameter estimation is not perfect, with kappa and beta consistently overestimated, and D underestimated. However, these discrepancies in parameter estimation counterbalance each other, resulting in a fitting outcome characterized by a low mean squared error. The absence of confidence intervals for models with 2 and 4 substages is attributed to structural inadequacy. As previously mentioned, the minimum possible value for kappa in the model is $\frac{1}{n}$. The model encounters limitations in aligning with a kappa value of 2/9 when using 2 and 4 substages. It is important to acknowledge the imprecision of parameter estimation, which will be a focus of our subsequent efforts.

@@

This is a citation \cite{Feng2016}

Another citation \cite{Anderson1991}

@@

\begin{figure}[h!]
    \centering
    \includegraphics{figures/mytest1.Rout.pdf}
    \caption{Mytest1 plot (are you working??)}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/distributionCompare.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/incidenceCompare.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/sametypeFittingL.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/sametypeFittingR.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

\subsection{Adaptability of the GCT Model to Data Input and Structural Changes in Fitting}
Proceeding to a more challenging test, we utilized a different model type for data generation and model fitting. As demonstrated in Figure x.x.A, the data generated by the LCT model with 2 substages were fitted using the GCT model with 12 substages. Despite the significant difference in model structure, the fitting results were reasonably favorable, with an MSE of 2.4. Altering the fitting model from a GCT with 2 substages to a GCT with 6 substages had negligible impact on the fitting outcomes (Figure x.x.B). Similarly, changing the input data from an LCT with 2 substages to an LCT with 7 substages resulted in slightly improved fitting, though the difference was not substantial (Figure x.x.C). These findings suggest that regardless of changes to the fitting model structure or the data used, the GCT model is capable of adapting to these variations, providing satisfactory fitting results.

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/difftypeFitting.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

\subsection{Parameter Estimation}
In this section, we discuss the parameter estimation results obtained through model fitting. The incidence data were generated using the GCT model with 5 substages, setting the $D$ to 10 and $\kappa$ to $\frac{2}{9}$. The model was fitted using the GCT framework with 5 to 10 substages. As depicted in Figure x.x, the precise values for each parameter are marked by a red line, with post-fitting parameter values displayed alongside their 95\% confidence intervals. It can be observed that the parameter estimation is not perfect, with kappa and beta consistently overestimated, and D underestimated. However, these discrepancies in parameter estimation counterbalance each other, resulting in a fitting outcome characterized by a low mean squared error. It is possible for the parameter to lack confidence intervals, which could be attributed to structural inadequacies. As previously mentioned, the minimum possible value for kappa in the model with $n$ substages is $\frac{1}{n}$. The model encounters limitations when aligning with a kappa value of less than $\frac{1}{n}$. Overall, it is important to acknowledge the imprecision of parameter estimation, which will be a focus of our subsequent efforts.

\begin{figure}[h]
    \centering
    \includegraphics[width= \textwidth]{figures/parEst.Rout.pdf}
    \caption{IMPORTANT}
\end{figure}

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width= \textwidth]{figures/mytest1.Rout.pdf}
    \caption{Mytest1 plot (are you working??)}
\end{figure}
